Fixing Vulnerabilities Potentially Hinders Maintainability

### 2021-07-14 paper/emse20.tex
adding acks

\section{Study Implications}\label{sec:implications}
%
Our results show evidence that developers may have to reduce maintainability for the 
sake of security. We argue that developers should be able to patch and produce 
secure code without hindering the maintainability of their projects. But there are 
still concerns that need to be addressed and that this study brings awareness for:
%
\textit{\textbf{Follow Best Practices:}} Developers are not 
paying attention to some quality aspects of their solutions/patches, 
as seen in Figure~\ref{fig:guidelines}, ending up harming 
software maintainability. We argue that developers
should design and implement solutions that respect the 
limit bounds of branch points and function/module sizes that are 
recommended by best practices to avoid increasing the 
size, complexity, and dependencies of their patches.
Developers should also keep function parameters below 
the recommended limit. It helps keep unit interfaces small 
and easy to use and understand.
Patterns such as \emph{Introduce Parameter Object} are useful 
to send information to a new function/class through an object
and keep the number of parameters small and the information well-organized.

@@

>>>>

\section{Study Implications}\label{sec:implications}
%
Our results show evidence that developers may have to reduce maintainability for the 
sake of security. We argue that developers should be able to patch and produce 
secure code without hindering the maintainability of their projects. But there are 
still concerns that need to be addressed and that this study brings awareness for:
%

\textit{\textbf{Follow Best Practices:}} Developers are not 
paying attention to some quality aspects of their solutions/patches, 
as seen in Figure~\ref{fig:guidelines}, ending up harming 
software maintainability. We argue that developers
should design and implement solutions that respect the 
limit bounds of branch points and function/module sizes that are 
recommended by best practices to avoid increasing the 
size, complexity, and dependencies of their patches.
Developers should also keep function parameters below 
the recommended limit. It helps keep unit interfaces small 
and easy to use and understand.
Patterns such as \emph{Introduce Parameter Object} are useful 
to send information to a new function/class through an object
and keep the number of parameters small and the information well-organized.

@@

\section*{Acknowledgements}

We thank SIG’s Better Code Hub team for all the support as
well as help in validating our methodology and results; and, Pedro Adão 
for the invaluable feedback in the early stages of the project.

This work is financed by National Funds through the
Portuguese funding agency, FCT - Fundação para a Ciência
e a Tecnologia with reference UIDB/50021/2020, a PhD scholarship 
(ref. SFRH/BD/143319/2019), the
SecurityAware Project (ref. CMU/TIC/0064/2019)---also funded
by the Carnegie Mellon Program---, and
the FaultLocker Project (ref. PTDC/CCI-COM/29300/2017).
